Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2020-05-19 PaperMagneticProfiles_JBSMSE.tex
Remove reference to supplementary material per JRB request.
Review and complete list of symbols.

\nomenclature[vm]{AMR}{Active Magnetic Regenerator}

@@

@@

\nomenclature[aq]{$\rate{q}\ped{csg}$}{volumetric casing losses in the AMR model [\si{\watt\per\cubic\meter}]}
\nomenclature[ic]{csg}{regenerator casing}
\nomenclature[ah]{$\hheat$}{heat transfer coefficient [\si{\watt\per\meter\squared\per\kelvin}]}
\nomenclature[aa]{$A\ped{sf}$}{contact surface area between solid and fluid phases in the regenerator [\si{\meter^2}]}
\nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
\nomenclature[bb]{$\beta$}{surface area density [\si{\square\meter\per\cubic\meter}]}
\nomenclature[ak]{$k$}{thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
\nomenclature[ad]{$D\ped{ld}$}{dispersion term in the AMR model [\si{\meter\square\per\second}]}
\nomenclature[af]{$f$}{cycle frequency [\si{\hertz}]}
\nomenclature[am]{$m$}{mass [\si{\kg}]}

@@

\begin{equation}
  \label{eq:58}
  \wvalve = N\ped{v}F\ped{B}\left(\wvalven + \frac{1}{2}\wrelayn\right)
\end{equation}

@@

\nomenclature[an]{$N\ped{valve}$}{number of valves}
\nomenclature[aw]{$\wvalve$}{valve power [\si{\watt}]}
\nomenclature[aw]{$\wvalven$}{nominal power comsumption of one valve [\si{\watt}]}
\nomenclature[aw]{$\wrelayn$}{nominal power comsumption of one relay [\si{\watt}]}

@@

\begin{equation}
  \label{eq:110}
  \Phi = \frac{\rate{m}\ped{f,max} F\ped{B} c\ped{f}}{2 f m\ped{s} c\ped{s}}
\end{equation}

@@

\nomenclature[azn]{$\etasec$}{second-law efficiency}
\section{Results and Discussions}
\label{sec:results-discussions}

@@

% \section*{Supplementary Material}
% \label{sec:suppl-mater}

% The datasets for the results shown in this paper, the source code used to produce the figures and the \LaTeX{} manuscript for this work are available at \cite{bib:fortkamp19-repo-pprof}.

% NA MINHA OPINIAO O SUPPLEMENTARY MATERIAL EH DESNECESSARIO

>>>>

\nomenclature[va]{AMR}{Active Magnetic Regenerator}

@@

\nomenclature[vd]{DoE}{design of experiments}

@@

\nomenclature[aq]{$\rate{q}\ped{csg}$}{volumetric casing losses in the AMR model [\si{\watt\per\cubic\meter}]}
\nomenclature[ic]{csg}{regenerator casing}
\nomenclature[ah]{$\hheat$}{heat transfer coefficient [\si{\watt\per\meter\squared\per\kelvin}]}
\nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
\nomenclature[bb]{$\beta$}{surface area density [\si{\square\meter\per\cubic\meter}]}
\nomenclature[ak]{$k$}{thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
\nomenclature[ad]{$D\ped{ld}$}{dispersion term in the AMR model [\si{\meter\square\per\second}]}
\nomenclature[af]{$f$}{cycle frequency [\si{\hertz}]}
\nomenclature[am]{$m$}{mass [\si{\kg}]}

@@

\begin{equation}
  \label{eq:58}
  \wvalve = N\ped{valve}F\ped{B}\left(\wvalven + \frac{1}{2}\wrelayn\right)
\end{equation}

@@

\nomenclature[an]{$N\ped{valve}$}{number of valves}
\nomenclature[awn]{$\wvalve$}{valve power [\si{\watt}]}
\nomenclature[awn]{$\wvalven$}{nominal power comsumption of one valve [\si{\watt}]}
\nomenclature[awn]{$\wrelayn$}{nominal power comsumption of one relay [\si{\watt}]}

@@

\begin{equation}
  \label{eq:110}
  \Phi = \frac{\rate{m}\ped{f,max} F\ped{B} c_{p,\mathrm{f}}}{2 f m\ped{s} c\ped{s}}
\end{equation}

@@

\nomenclature[bn]{$\etasec$}{second-law efficiency}
\section{Results and Discussions}
\label{sec:results-discussions}

@@
